Facility and Time Step Discretization Effects in Fuel Cycle Simulation

### 2015-09-28 paper.tex
clarify drawdown explanation
discuss jit ordering and its affect on fuel utilization

One important phenomenon related to time step duration is the \emph{inventory
drawdown effect}.  Increasing time step duration reduces the frequency over
which refueling can occur, resulting in larger impulse drawdown on
inventories. This by itself is not problematic because this is balanced by
correspondingly larger inventory top-up quantities.  The other component of
this effect is the simultaneity of incoming and outgoing material flows on a
given time step.  Within a particular time step facilities do not know about
incoming material when they make commitments for outgoing material.  For
longer time steps, larger incoming quanta of material are not available for
making offers. In general longer time steps and individual reactor modeling
create a need for larger floating inventory buffers in order to avoid material
shortages.  Although direct measures of this effect are difficult, some of its
consequences can be quantified by comparing scenarios with different time step
durations (e.g. cases 2 and 4) such as higher standing inventories during
shortages.

@@

Figure \ref{fig:puinv-compare} shows the same inventory curves from Figure
\ref{fig:puinv} superimposed. Counter-intuitively, lower separated plutonium
inventory during the shortage generally indicates fewer unfueled reactors.
Lower inventory levels mean available Pu is being utilized more efficiently
rather than sitting idle.  Cases 3 and 4 with their longer time steps show
higher inventories indicating a more severe shortage.  Post shortage, they
also fall a bit behind on building up Pu stocks due to the delayed
contributions of more unfueled reactors to the separated Pu pool.

>>>>

One important phenomenon related to time step duration is the \emph{inventory
drawdown effect}.  Increasing time step duration reduces the frequency over
which refueling can occur, resulting in larger impulse drawdown on
inventories. This by itself is not problematic because this is balanced by
correspondingly larger inventory top-up quantities.  The other component of
this effect is the simultaneity of incoming and outgoing material flows on a
given time step.  Within a particular time step facilities do not know about
incoming material when they make commitments for outgoing material.  For
longer time steps, larger incoming quanta of material are not available for
making offers. In general longer time steps and individual reactor modeling
create a need for larger floating inventory buffers in order to avoid material
shortages.  Another way to think about this effect is that a single material
object can only move between a single pair of facilities per time step. Larger
time steps result in longer minimum bounds on time to traverse paths between
facilities. Although direct measures of this effect are difficult, some of its
consequences can be quantified by comparing scenarios with different time step
durations (e.g. cases 2 and 4) such as higher standing inventories during
shortages.

@@

Figure \ref{fig:puinv-compare} shows the same inventory curves from Figure
\ref{fig:puinv} superimposed. Counter-intuitively, lower separated plutonium
inventory during the shortage generally indicates fewer unfueled reactors.
Lower inventory levels mean available Pu is being utilized more efficiently
rather than sitting idle.  Cases 3 and 4 with their longer time steps show
higher inventories indicating a more severe shortage.  Post shortage, they
also fall a bit behind on building up Pu stocks due to the delayed
contributions of more unfueled reactors to the separated Pu pool.  The
reactors in these scenarios request fresh fuel only when they need it. While
this is an unrealistic behavior for real-world facilities, it is closer to a
globally optimum fuel management strategy.  Keeping on-hand fresh fuel batches
would also have the same effect of increasing idling plutonium quantities and
making the fuel shortage worse overall.
